Neural models for computer-assisted musical orchestration: a preliminary study

### 2020-05-14 paper/latex/paper.tex
Add orchestration results data

\begin{table*}
  \begin{center}
    \label{orch_eval}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|} 
    	  \hline
      \textbf{Model} & \textbf{Ob + Bn} & \textbf{Bn} & \textbf{Bass Clarinet} & \textbf{Bell1} & \textbf{Bell2} & \textbf{Yan} & \textbf{Car Horn} & \textbf{Boat}  \\
      \hline
      CNN with LSTM & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
      \hline
      ResNet & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
      \hline
      OrchIdea & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
      \hline
      \hline
      \textbf{Model} & \textbf{Wind Harp} & \textbf{Chord1} & \textbf{Reed Bone} & \textbf{Chord2} & \textbf{Gong} & \textbf{Scream} & \textbf{Trompe Attack} & \textbf{Average}  \\
      \hline
      CNN with LSTM & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
      \hline
      ResNet & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
      \hline
      OrchIdea & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Quantitative comparison of orchestrations.}
\end{table*}

>>>>

\begin{table*}
  \begin{center}
    \label{orch_eval}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|} 
    	  \hline
      \textbf{Model} & \textbf{Ob + Bn} & \textbf{Bn} & \textbf{Bass Clarinet} & \textbf{Bell1} & \textbf{Bell2} & \textbf{Yan} & \textbf{Car Horn} & \textbf{Boat}  \\
      \hline
      CNN with LSTM & 0.17 & 0.28 & 0.70 & 0.55 & 0.26 & \textbf{1.10} & 0.68 & \textbf{1.12} \\
      \hline
      ResNet & 0.34 & 0.50 & 0.48 & 0.59 & 0.45 & 0.90 & 0.49 & \textbf{1.16} \\
      \hline
      OrchIdea & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\
      \hline
      \hline
      \textbf{Model} & \textbf{Wind Harp} & \textbf{Chord1} & \textbf{Reed Bone} & \textbf{Chord2} & \textbf{Gong} & \textbf{Scream} & \textbf{Trompe Attack} & \textbf{Average}  \\
      \hline
      CNN with LSTM & 0.55 & - & 0.70 & - & 0.73 & \textbf{1.14} & 0.79 & 0.59\\
      \hline
      ResNet & 0.61 & - & 0.51 & - & 0.71 & \textbf{1.03} & \textbf{1.05} & 0.55 \\
      \hline
      OrchIdea & 1 & - & 1 & - & 1 & 1 & 1 & 1 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Quantitative comparison of orchestrations as ratios to OrchIdea. Eqn. \eqref{distance} was used with $\lambda_1 = 0.5$ and $\lambda_2 = 10$ to compute distances between orchestrations and targets. What is shown is the the ratio between the distance calculated and OrchIdea's distance for the same target. A value less than 1 means that the model performed worse (i.e. had a larger distance), and a value greater than 1 means the model performed better than OrchIdea. "Average" is the ratio of the average distances for the model across all targets.}
\end{table*}
